\begingroup
\renewcommand{\section}[2]{}  
\begin{thebibliography}{99}

\bibitem{Branson2010VisualRW}
Branson, S., Wah, C., Schroff, F., Babenko, B., Welinder, P., Perona, P., Belongie, S. J. (2010), 
“Visual Recognition with Humans in the Loop”, 
trong European Conference on Computer Vision.

\bibitem{Cao2021}
Cao, Q., Zhao, Z., Zeng, Q., Wang, Z., Long, K. (2021), 
“Real-Time Vehicle Trajectory Prediction for Traffic Conflict Detection at Unsignalized Intersections”, 
Journal of Advanced Transportation, 2021, tr.1--15.

\bibitem{Chen2021}
Chen, C., Guo, J., Guo, C., Chen, C., Zhang, Y., Wang, J. (2021), 
“Adaptive Cruise Control for Cut-In Scenarios Based on Model Predictive Control Algorithm”, 
Applied Sciences, 11(11), tr.5293.

\bibitem{Coskun2024}
Co{\c{s}}kun, A., Bilicz, S. (2024), 
“Data-Driven Clustering and Classification of Road Vehicle Radar Scattering Characteristics Using Histogram-Based RCS Features”, 
Electronics, 13(4), tr.759.

\bibitem{Du2022ImprovedRT}
Du, L., Chen, X., Pei, Z., Zhang, D., Liu, B., Chen, W. (2022), 
“Improved Real-Time Traffic Obstacle Detection and Classification Method Applied in Intelligent and Connected Vehicles in Mixed Traffic Environment”, 
Journal of Advanced Transportation.

\bibitem{VectorNet2020}
Gao, J., Sun, C., Zhao, H., Shen, Y., Anguelov, D., Li, C., Schmid, C. (2020), 
“VectorNet: Encoding HD Maps and Agent Dynamics from Vectorized Representation”, 
trong Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR).

\bibitem{He2023VehicleDI}
He, D., Zhao, M., Wang, Z. (2023), 
“Vehicle Driving Intent Recognition Based on Enhanced Bidirectional Long Short-Term Memory Network”, 
Journal of Artificial Intelligence Practice.

\bibitem{Hidayatullah2025YOLOv8TY}
Hidayatullah, P., Syakrani, N., Sholahuddin, M. R., Gelar, T., Tubagus, R. (2025), 
“YOLOv8 to YOLO11: A Comprehensive Architecture In-Depth Comparative Review”, 
arXiv preprint arXiv:2501.13400.

\bibitem{Huang2014}
Huang, A., Xu, L., Li, Y., Chen, E. (2014), 
“Robust Dynamic Trajectory Regression on Road Networks: A Multi-Task Learning Framework”, 
trong 2014 IEEE International Conference on Data Mining (tr.845--850), IEEE.

\bibitem{Ibarra2016}
Ibarra Arenado, M. (2016), 
“Detecci{\'o}n y localizaci{\'o}n de veh{\'\i}culos mediante sombras en la carretera basada en visi{\'o}n por computador”, 
Luận án tiến sĩ, Universidad de Cantabria.

\bibitem{yolov8_ultralytics}
Jocher, G., Chaurasia, A., Qiu, J. (2023), 
Ultralytics YOLOv8 (Version 8.0.0), 
https://github.com/ultralytics/ultralytics, 
truy cập ngày 24/03/2026.

\bibitem{yolo26_ultralytics}
Jocher, G., Qiu, J. (2026), 
Ultralytics YOLO26 (Version 26.0.0), 
https://github.com/ultralytics/ultralytics, 
truy cập ngày 24/03/2026.

\bibitem{Kumar2023}
Kumar, S., Singh, S. K., Varshney, S., Singh, S., Kumar, P., Kim, B.-G., Ra, I.-H. (2023), 
“Fusion of Deep Sort and Yolov5 for Effective Vehicle Detection and Tracking Scheme in Real-Time Traffic Management Sustainable System”, 
Sustainability, 15(24), tr.16869.

\bibitem{Lefvre2014ASO}
Lef{\`e}vre, S., Vasquez, D., Laugier, C. (2014), 
“A survey on motion prediction and risk assessment for intelligent vehicles”, 
ROBOMECH Journal, 1.

\bibitem{Lim2018}
Lim, Q., Lim, Y., Muhammad, H., Tan, D. W. M., Tan, U.-X. (2018), 
“Forward collision warning system for motorcyclist using smart phone sensors based on time-to-collision and trajectory prediction”, 
Journal of Engineering.

\bibitem{Lv2023DETRsBY}
Lv, W., Xu, S., Zhao, Y., Wang, G., Wei, J., Cui, C., Du, Y., Dang, Q., Liu, Y. (2023), 
“DETRs Beat YOLOs on Real-Time Object Detection”, 
trong 2024 IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR) (tr.16965--16974).

\bibitem{Mohsen2021Industry4D}
Mohsen, S., Elkaseer, A., Scholz, S. G. (2021), 
“Industry 4.0-Oriented Deep Learning Models for Human Activity Recognition”, 
IEEE Access, 9, tr.150508--150521.

\bibitem{VisionTrap2024}
Moon, S., Woo, H., Park, H., Jung, H. và cộng sự (2024), 
“VisionTrap: Vision-Augmented Trajectory Prediction Guided by Textual Descriptions”, 
arXiv preprint arXiv:2407.12345.

\bibitem{Mozaffari2020DeepLV}
Mozaffari, S., Al-Jarrah, O. Y., Dianati, M., Jennings, P., Mouzakitis, A. (2020), 
“Deep Learning-Based Vehicle Behavior Prediction for Autonomous Driving Applications: A Review”, 
IEEE Transactions on Intelligent Transportation Systems, 23, tr.33--47.

\bibitem{Pae2018}
Pae, D. S., Choi, I. H., Kang, T. K., Lim, M. T. (2018), 
“Vehicle Detection Framework for Challenging Lighting Driving Environment Based on Feature Fusion Method Using Adaptive Neuro-Fuzzy Inference System”, 
International Journal of Advanced Robotic Systems, 15(2).

\bibitem{Paravarzar2020}
Paravarzar, S., Mohammad, B. (2020), 
“Motion Prediction on Self-driving Cars: A Review”, 
arXiv preprint arXiv:2011.03635.

\bibitem{Sapkota2025UltralyticsYE}
Sapkota, R., Karkee, M. (2025), 
“Ultralytics YOLO Evolution: An Overview of YOLO26, YOLO11, YOLOv8 and YOLOv5 Object Detectors for Computer Vision and Pattern Recognition”, 
arXiv preprint arXiv:2510.09653.

\bibitem{virtual_bumper}
Schiller, W., Donath, M. (1997), 
“The Virtual Bumper: A Control-Based Collision Avoidance System for Highway Vehicles”, 
Minnesota Department of Transportation.

\bibitem{Shneiderman2020HumanCenteredAI}
Shneiderman, B. (2020), 
“Human-Centered Artificial Intelligence: Reliable, Safe \& Trustworthy”, 
International Journal of Human–Computer Interaction, 36, tr.495--504.

\bibitem{Redmon2015YouOL}
Redmon, J., Divvala, S. K., Girshick, R. B., Farhadi, A. (2016), 
“You Only Look Once: Unified, Real-Time Object Detection”, 
trong 2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR) (tr.779--788).

\bibitem{ti_svc}
Texas Instruments (2015), 
“Surround View Camera Systems for ADAS”, 
https://www.ti.com/lit/wp/spry270a/spry270a.pdf, 
truy cập ngày 24/03/2026.

\bibitem{Ullah2018ActionRI}
Ullah, A., Ahmad, J., Muhammad, K., Sajjad, M., Baik, S. W. (2018), 
“Action Recognition in Video Sequences Using Deep Bi-Directional LSTM With CNN Features”, 
IEEE Access, 6, tr.1155--1166.

\bibitem{Ultralytics}
Ultralytics, 
Ultralytics GitHub repository, 
https://github.com/ultralytics/ultralytics, 
truy cập ngày 24/03/2026.

\bibitem{Wan2021}
Wan, X., Zhou, S., Wang, J., Meng, R. (2021), 
“Multiple Object Tracking by Trajectory Map Regression with Temporal Priors Embedding”, 
trong Proceedings of the 29th ACM International Conference on Multimedia (tr.1--9).

\bibitem{THU-MIGyolov10}
Wang, A., Chen, H., Liu, L. và cộng sự (2024), 
“YOLOv10: Real-Time End-to-End Object Detection”, 
arXiv preprint arXiv:2405.14458.

\bibitem{Wang2024YOLOv9LW}
Wang, C.-Y., Yeh, I.-H., Liao, H. (2024), 
“YOLOv9: Learning What You Want to Learn Using Programmable Gradient Information”, 
arXiv preprint arXiv:2402.13616.

\bibitem{Wang2021}
Wang, J., Wang, P., Zhang, C., Su, K., Li, J. (2021), 
“Fusion Neural Network for Vehicle Trajectory Prediction in Autonomous Driving”, 
trong ICASSP 2021 - 2021 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP).

\bibitem{Young2016}
Young, A., Marshall, S., Gray, A. (2016), 
“Outlier and Target Detection in Aerial Hyperspectral Imagery: A Comparison of Traditional and Percentage Occupancy Hit or Miss Transform Techniques”, 
trong Target and Background Signatures II (tr.10000), SPIE.

\bibitem{Zarei2023}
Zarei, N., Moallem, P., Shams, M. (2023), 
“Real-Time Vehicle Detection Using Segmentation-Based Detection Network and Trajectory Prediction”, 
IET Computer Vision, 17(2), tr.207--220.

\bibitem{Zeng2025TrajectoryPF}
Zeng, L., Chen, F., Li, J., Wang, H., Li, Y., Zhai, Z. (2025), 
“Trajectory Prediction for Powered Two-Wheelers in Mixed Traffic Scenes: An Enhanced Social-GAT Approach”, 
Systems.

\bibitem{TNT2020}
Zhao, H., Gao, J., Lan, T., Sun, C., Sapp, B. (2020), 
“TNT: Target-Driven Trajectory Prediction”, 
trong Conference on Robot Learning (CoRL).

\end{thebibliography}
\endgroup